### 2021-01-20 cv/cv-body.tex
Add preprint link
Add paper
Add doi
Add MP SAR

@@

at PLOS Computational Biology. medRxiv preprint:

@@

(\href{https://www.dropbox.com/s/y8b0rlxvnodngf8/Anderson_etal_2020_reproducible_visualization.pdf?dl=1}{PDF})

@@

\begin{description}
\tightlist
\item[2020]
Haggarty D.R., Q.C. Huynh, R.E. Forrest, \textbf{S.C. Anderson}, M.J.
Bresch, E.A. Keppel. Evaluation of potential rebuilding strategies for
Inside Yelloweye Rockﬁsh (\emph{Sebastes ruberrimus}) in British
Columbia. Accepted as a DFO Can. Sci. Advis. Sec. Res. Doc. on June 11
2020.
(\href{https://www.dropbox.com/s/pll8axzsxqka8j8/resdoc-iye.pdf?dl=1}{English
version}).
\item[2020]
\textbf{Anderson, S.C.}, R.E. Forrest, Q.C. Huynh, E.A. Keppel. A
management procedure framework for groundﬁsh in British Columbia.
Accepted as a DFO Can. Sci. Advis. Sec. Res. Doc. on June 9 2020.
(\href{https://www.dropbox.com/s/rgxk2wco5v5zp0e/gfmp-2020-03-13.pdf?dl=1}{English
version}).
\item[2020]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. DFO Can. Sci. Advis. Sec. Res. Doc. 2020/070 iv +
204 p.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-fra.html}{French
version}).
\item[2019]
\textbf{Anderson, S.C.}, E.A. Keppel, A.M. Edwards, 2019. A reproducible
data synopsis for over 100 species of British Columbia groundfish. DFO
Can. Sci. Advis. Sec. Res. Doc. 2019/041. vii + 321 p.
(\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-eng.html}{English
version},
\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-fra.html}{French
version}).
\end{description}

>>>>

Barnett, L.A.K., E.J. Ward, \textbf{S.C. Anderson}. Improving estimates
of species distribution change by incorporating local trends. In press
at Ecography. \url{https://doi.org/10.1111/ecog.05176}.

@@

at PLOS Computational Biology:
\url{https://doi.org/10.1371/journal.pcbi.1008274}. medRxiv preprint:

@@

(\href{https://www.dropbox.com/s/4mmnomvmpg0dbky/Anderson_etal_2020_reproducible_visualization_preprint.pdf?dl=1}{Preprint
PDF})

@@

\begin{description}
\tightlist
\item[2020]
Haggarty D.R., Q.C. Huynh, R.E. Forrest, \textbf{S.C. Anderson}, M.J.
Bresch, E.A. Keppel. Evaluation of potential rebuilding strategies for
Inside Yelloweye Rockﬁsh (\emph{Sebastes ruberrimus}) in British
Columbia. Accepted as a DFO Can. Sci. Advis. Sec. Res. Doc. on June 11
2020.
(\href{https://www.dropbox.com/s/pll8axzsxqka8j8/resdoc-iye.pdf?dl=1}{English
version}).
\item[2020]
\textbf{Anderson, S.C.}, R.E. Forrest, Q.C. Huynh, E.A. Keppel. A
management procedure framework for groundﬁsh in British Columbia.
Accepted as a DFO Can. Sci. Advis. Sec. Res. Doc. on June 9 2020.
(\href{https://www.dropbox.com/s/rgxk2wco5v5zp0e/gfmp-2020-03-13.pdf?dl=1}{English
version}).
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/SAR-AS/2021/2021_002-eng.html}{Associated
Science Advisory Report}.
\item[2020]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. DFO Can. Sci. Advis. Sec. Res. Doc. 2020/070 iv +
204 p.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-fra.html}{French
version}).
\item[2019]
\textbf{Anderson, S.C.}, E.A. Keppel, A.M. Edwards, 2019. A reproducible
data synopsis for over 100 species of British Columbia groundfish. DFO
Can. Sci. Advis. Sec. Res. Doc. 2019/041. vii + 321 p.
(\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-eng.html}{English
version},
\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-fra.html}{French
version}).
\end{description}
